%-------------------------
% Resume in Latex
% Author : Ravi Ranjan
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Ravi Ranjan} \\ \vspace{4pt}
    \small {Contact: \underline{+91-8389057954}} $|$ \href{mailto:ranjanjharavi@gmail.com}{Email: \underline{ranjanjharavi}@gmail.com} $|$ $|$
    \href{https://linkedin.com/in/ranjanjharavi}{Linkedin: \underline{ranjanjharavi}} $|$
    \href{https://github.com/ranjanjharavi}{Github : \underline{ranjanjharavi}}
\end{center}


%-----------EDUCATION-----------
\vspace{1pt}
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Maulana Abul Kalam Azad University of Technology (Formerly WBUT)}{W.B, India}
      {Bachelor of Technology in Computer Science and Engineering; \underline{GPA}: 7.58/10}{Aug. 2013 -- Jul. 2017}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Advanced Computer Software Group Ltd.}{Mar. 2018 -- Present}
      {Software Engineer}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{{\textbf{Docman 10} $|$ \emph{ C\texttt{\#}, ASP.NET MVC, JavaScript, MySQL, jQuery, Redis, React.js, AWS}}}
        \resumeItemListStart
            \resumeItem{Developed features and Rest API for multiple modules including 3rd party integration for the product.}
            \resumeItem{Improved the response time by 40\% of the audit history by writing efficient stored procedures and algorithms.}
            \resumeItem{Involved in the deployment of web services.}
      \resumeItemListEnd
      
      \vspace{7pt}
      
        \resumeItem{{\textbf{CareSys} $|$ \emph{ C\texttt{\#}, VB.NET, MS-SQL, JavaScript, WinForms}}}
        \resumeItemListStart
            \resumeItem{Developed features to enforce the GDPR in the product and hence the NPS score of the product increased. }
            \resumeItem{Fixed 86\% of bugs and existing defects for which received the spot award.}
        \resumeItemListEnd
        
              \vspace{7pt}
      
        \resumeItem{{\textbf{Payana } $|$ \emph{ C\texttt{\#}, ASP.NET MVC, MS-SQL, JavaScript, React.js}}}
        \resumeItemListStart
            \resumeItem{Developed a full-stack web application during training period for travel request by an employee and approval by their line manager for different working location.}
            \resumeItem{Developed UI and API endpoints for the Handwritten recognition applet part of Advanced hackathon.}
        \resumeItemListEnd
        
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------

\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Open Live Writer (.NET Foundation)} $|$ \emph{ C\texttt{\#}.NET, WinForms}}{Oct. 2019}
          \resumeItemListStart
            \resumeItem{Contributed to this Open Source WYSIWYG project by fixing 4 bugs part of Hacktoberfest.}
            \resumeItem{Fixed embedding of Youtube URLs, keybindings problems with different windows.}
            \resumeItem{Improved the layout during multiple images import}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Hostel Management System} $|$ \emph{C\texttt{\#}, ASP.NET MVC, JavaScript, MySQL}}{Dec. 2016 -- Mar. 2017}
          \resumeItemListStart
            \resumeItem{Developed student allocation system to allocate students based on multiple filters.} 
            \resumeItem{Created student profiles and information about rooms, canteens, etc.}
            \resumeItem{Created forums with polls where students can discuss interact.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Sub-Network Design} $|$ \emph{RHEL, LAMP Server, JavaScript }}{Jul. 2016}
          \resumeItemListStart
            \resumeItem{Designed and implemented a sub-network involving 46 computers, 2 virtual routers, 4 servers including Web, Mail, DNS and Samba, and created firewall rules.} 
            \resumeItem{This network and website had facilities for user access according to the hierarchy of their positions in their company portfolio which could be accessed from the outside world.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------Certificates & Awards-----------

\section{Certificates \& Awards}
 \begin{itemize}[leftmargin=0.15in, label={}]
 \item {
    \resumeItemListStart
         \resumeItem{Received Spot Award given quarterly to high performing individuals at Advanced.}
         \resumeItem{Qualified Graduate Aptitude Test in Engineering (GATE) 2018.}
         \resumeItem {Awarded certificate of achievement in Entrepreneurship week 2014 by National Entrepreneurship Network (NEN).}
         \resumeItem { Awarded Certificate of completion with 95\% in “C++ for C Programmers - Part A” by Coursera.}
     \resumeItemListEnd
     }
 \end{itemize}


%
%-----------PROGRAMMING SKILLS-----------

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C\texttt{\#}, JavaScript, C/C++, SQL, NoSQL, HTML/CSS.} \\
     \textbf{Technologies}{: ASP.NET MVC, React, jQuery, AWS, Git, Firebase, JIRA.} \\
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
